Proposed Solution

### 2017-01-25 CAV17/secs/learner.tex
autocommit

For any relation that violates a known rule, the checker will output the predicate and keyword sets associated with that rule, as well as the learned support and confidence values.
Since this is a probabilistic approach, in our implementation \app, we provide the user with these values to determine if they rule must be satisfied in their application on a case-by-case basis.
For instance, the \texttt{key\_buffer} misconfiguration from Sec. \ref{ex:fine} will only be noticeable if the application experiences a heavy traffic load, so the user may choose to ignore this error if they are confident this will not be an issue.

\subsection{Implementation}

@@

Once the program has finished merging together a set of built relations over every example file in the learning set, we have implemented a \textit{check} function for each of the rules, where we input the group of entities under which a relation is defined, the expected observation on that relation, and the actually observed observation in the file we are checking. If the observed instance is inconsistent with the relations built from our training set files, then we would see it reported. In the probablistic setting of our tool, we would implement cutoffs to tune our \textit{check} to ignore observed relations under a certain significance level.

>>>>

For any relation from the verification target that violates a known rule, the checker will report the predicate and keyword sets associated with that rule as an error.
Since this is a probabilistic approach, in our tool \app, we provide the user with the support and confidence values as well to help the user determine if the rule must be satisfied in their particular system.
For instance, the \texttt{key\_buffer} misconfiguration from Sec. \ref{ex:fine} will only be noticeable if the system experiences a heavy traffic load, so the user may choose to ignore this error if they are confident this will not be an issue.

\iffalse
\subsection{Implementation}

@@

Once the program has finished merging together a set of built relations over every example file in the learning set, we have implemented a \textit{check} function for each of the rules, where we input the group of entities under which a relation is defined, the expected observation on that relation, and the actually observed observation in the file we are checking. If the observed instance is inconsistent with the relations built from our training set files, then we would see it reported. In the probablistic setting of our tool, we would implement cutoffs to tune our \textit{check} to ignore observed relations under a certain significance level.
\fi
